---
title: "Retirement Calculator"
author: "Diego Saenz"
date: "Friday, August 01, 2014"
output: html_document
runtime: shiny
---

This is my first crack at using an R Markdown document made interactive using Shiny.  

To go to the home page, [click here](http://www.anotherfrugalengineer.com).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r, echo=FALSE}
inputPanel(
  selectInput("savings_rate", label = "Savings Rate:",
              choices = c(0, 10, 20, 30, 40, 50, 60, 70, 80), selected = 20),
  
  sliderInput("age", label = "Age:",
              min = 0, max = 100, value = 25, step = 1)

)

renderPlot({
  age <- as.numeric(input$age)
  s <- as.numeric(input$savings_rate) / 100 #savings rate
  end <- 100
  years <- c(age:end)
  assets <- seq(age:end)
  income <- 100000 #post tax income
  assets[1] <- 250000
  r <- 0.07 #returns
  i <- 0.03  #inflation
  n <- 2
  while(assets[n-1] < (income * (1 - s)) / (r - i)){
    income <- income * (1 + i)
    assets[n] <- assets[n-1] * (1 + r) + income * s
    n <- n + 1  
  }
  retire <- age + n - 1
  while(n < end - age + 2){
    income <- income * (1 + i)
    assets[n] <- assets[n-1] * (1 + r) - income * (1 - s)
    n <- n + 1
  }
  plot(years, assets, col = "blue")
})
```

## Retirement Age

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



